Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-20 manuscript/main.tex
Fixed a reference to the best model missed in the last commit
Add methods for alternate DMS metrics and rename primary metric in tables

\begin{figure*}[p]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/test-of-best-model-for-natural-populations.png}
  \caption{
  Test of best model for natural populations of A/H3N2 viruses, the composite model of HI cross-immunity and mutational load.
  A) The correlation of estimated and observed clade growth rates shows the model's ability to capture clade-level dynamics without explicitly optimizing for clade frequency targets.
  B) The rank of the estimated best strain based on its distance to the future for 8 timepoints.
  The estimated best strain was in the top 20th percentile of observed closest strains for 88\% of timepoints.
  C) Absolute forecast error for clades shown in A by their initial frequency with a mean LOESS fit (solid black line) and 95\% confidence intervals (grey shading) based on 100 bootstraps.
  D) The correlation of all strains at all timepoints by the percentile rank of their observed and estimated distances to the future.
  }
  \label{fig:test_of_best_model_for_natural_populations}
  \end{center}
\end{figure*}

@@

>>>>

\begin{figure*}[p]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/test-of-best-model-for-natural-populations.png}
  \caption{
  Test of best model for natural populations of A/H3N2 viruses, the composite model of HI cross-immunity, mutational load, and LBI.
  A) The correlation of estimated and observed clade growth rates shows the model's ability to capture clade-level dynamics without explicitly optimizing for clade frequency targets.
  B) The rank of the estimated best strain based on its distance to the future for 8 timepoints.
  The estimated best strain was in the top 20th percentile of observed closest strains for 88\% of timepoints.
  C) Absolute forecast error for clades shown in A by their initial frequency with a mean LOESS fit (solid black line) and 95\% confidence intervals (grey shading) based on 100 bootstraps.
  D) The correlation of all strains at all timepoints by the percentile rank of their observed and estimated distances to the future.
  }
  \label{fig:test_of_best_model_for_natural_populations}
  \end{center}
\end{figure*}

@@

To determine whether DMS preferences could be used to define fitness metrics that were less dependent on the historical context of the background strain, we implemented two additional DMS-based metrics: ``DMS entropy'' and ``DMS mutational load''.
For both metrics, we calculated the distance between HA amino acid sequences of each strain and its ancestral sequence in the previous season, to enable comparison of these metrics with the DMS mutational effects and mutational load metrics.
For the ``DMS entropy'' metric, we calculated the distance between sequences such that each mismatch was weighted by the inverse entropy of DMS preferences at the site of the mismatch.
We expected this metric to produce a negative coefficient similar to the mutational load metric, as higher values will result from mutations at sites with lower entropy and, thus, lower tolerance for mutations.
For the ``DMS mutational load'' metric, we defined a novel set of non-epitope sites corresponding to each position in HA with a standardized entropy less than zero.
With this metric, we sought to identify more highly conserved sites without weighting any one site differently from others.
We anticipated that this lack of site-specific weighting would make the DMS mutational load metric even less background-dependent than the DMS entropy and DMS mutational effect metrics.
